---
title: 'Outline: The windows of opportunity for drug therapy against SARS-CoV-2 infection'
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
---

# setup
```{r setup, include=F}
library(deSolve)
library(tidyverse)
library(magrittr)
library(mlxR)
library(data.table)
library(hrbrthemes)
library(pkr)
library(ggplot2)
library(ggsci)
library(gridExtra)
library(gtable)

# function to make word document out of data.frame
df2word <- function(df, output_file = "table.doc", output_dir = ".", ...) {
  f <- tempfile(fileext =".Rmd" )
  cat(file = f, '```{r, echo = FALSE}
                  knitr::kable(df)
                 ```', append = TRUE)
  rmarkdown::render(f, output_file = output_file, output_dir = output_dir, ...)
  unlink(f)
  file.path(output_dir, output_file)
}
```

# Methods
## Viral kinetics
In the standard target cell limited model, an inoculum of virus particles *V* infects a pool of target cells *T* with rate *$\beta$*. Infected cells begin shedding virions at rate *p*. The parameters *c* and *$\delta$* determine the rate of loss for virus and cell death, respectively. We also considered an extension of this model in which infected cells enter an eclipse phase (*E*) for an average duration *$1/k$* until they begin shedding.

The viral kinetics models predict absolute viral loads. The authors reported the cycle threshold (Ct) value from real time polymerase chain reaction (rtPCR) assays. As these vary by laboratory and analytical conditions,  we chose to correlate model output with observed Ct values with a regression model described by Chou et al., Clin Chem. 2020; 66: 549-555): Ct(load [log10]) = -3.502*load + 40.55

```{r}
Ct_viral_load <- function( Ct, viral_load ) {
  if( missing(Ct) )
    return (-3.502*viral_load+40.55)
  
  return( (Ct-40.55)/-3.502 )
}

Ct_viral_load( viral_load=3.0 )
Ct_viral_load( Ct=30 )
```

Positivity in rtPCR was set at a Ct value of 35.

"Detection of SARS-CoV-2 in Different Types of Clinical Specimens"
Wenling Wang, PhD1; Yanli Xu, MD2; Ruqin Gao, MD3; et al Roujian Lu, MPH1; Kai Han, BS2; Guizhen Wu, MD1; Wenjie Tan, MD, PhD1
Author Affiliations Article Information
JAMA. 2020;323(18):1843-1844. doi:10.1001/jama.2020.3786 

```{r}
CT_LIMIT_OF_DETECTION <- 35
```


```{r echo=F, fig.width=5, fig.height=3}
# manual fit
IgG_RBD_To_EC50 <- 12 # days
IgG_RBD_To_Emax <- 2.1 # IgG level
IgG_RBD_To_Hill <- 8 # Hill coefficient
IgG_RBD_To_max_eps <- 42 # maximum effect on viral clearance
IgG_RBD_response <- data.frame( days = 0:60,
                                IgG_RBD = ((0:60)^IgG_RBD_To_Hill)/(IgG_RBD_To_EC50^IgG_RBD_To_Hill+(0:60)^IgG_RBD_To_Hill))

ggplot(IgG_RBD_response %>% filter(days<31), aes(days, IgG_RBD_To_Emax*IgG_RBD) ) + # scaled to optical densities reported
  geom_line() + 
  labs( title="Anti-RBD IgG production",
        subtitle="Data: Lancet Infect Dis. 2020;20(5):565-574, Fig. 4",
        x="Time [d]",
        y="Optical density")
#theme_ipsum_ps()
```

```{r}
IgG_Long_EC50 <- 10.2 # days
IgG_Long_Emax <- 104.6 
IgG_Long_Hill <- 3.4 # Hill coefficient
IgG_Long_max_eps <- 52 #from Nelder Mead #42 # maximum effect on viral clearance
IgG_Long_response <- data.frame( days = 0:60,
                                 IgG_Long = ((0:60)^IgG_Long_Hill)/(IgG_Long_EC50^IgG_Long_Hill+(0:60)^IgG_Long_Hill))

ggplot(IgG_Long_response %>% filter(days<31), aes(days, IgG_Long_Emax*IgG_Long) ) + # scaled to optical densities reported
  geom_line() + 
  labs( title="Seroconversion",
        subtitle="Data: Nat Med 26, 845–848 (2020)",
        x="Time [d]",
        y="Converted [%]")
#theme_ipsum_rc()
```


## Pharmacokinetic models
### IVM
from Duthaler et al., 2020.

####PK model
```{r echo=F}
ivmfood.model <- inlineModel("
[INDIVIDUAL]
input = { NN_pop, Mtt_pop, ka_pop, Cl_pop, V1_pop, Q_pop, V2_pop, F1_pop,
          NN_sd, Mtt_sd, ka_sd, Cl_sd, V1_sd, Q_sd, V2_sd,
          prop, add,
          WT }

EQUATION:
covWT = log(WT) - 4.248495 ; centered on log(70)
F1 = F1_pop

DEFINITION:
NN  = { distribution=lognormal, typical=NN_pop,   sd=NN_sd }
Mtt = { distribution=lognormal, typical=Mtt_pop,  sd=Mtt_sd }
ka  = { distribution=lognormal, typical=ka_pop,   sd=ka_sd }
Cl  = { distribution=lognormal, typical=Cl_pop,   sd=Cl_sd,   covariate=covWT,  coefficient=0.75 }
V1  = { distribution=lognormal, typical=V1_pop,   sd=V1_sd,   covariate=covWT,  coefficient=1 }
Q   = { distribution=lognormal, typical=Q_pop,    sd=Q_sd }
V2  = { distribution=lognormal, typical=V2_pop,   sd=V2_sd }

[LONGITUDINAL]
input = { NN, Mtt, ka, Cl, V1, Q, V2, F1, prop, add, WT}

EQUATION:
odeType = stiff
ddt_AUC = 1/V1 * Ac

; Parameter transformations 
Ktr = (NN+1)/Mtt
V = V1 
k = Cl/V1 
k12 = Q/V1 
k21 = Q/V2

; PK model definition
PK:
compartment(cmt=1, amount=Ac, volume=V)
peripheral( k12, k21 )
elimination( k )
oral( cmt=1, ka, Mtt, Ktr, p=F1 )
Cc = Ac / V

OUTPUT:
output = {Cc, y, AUC, WT}

DEFINITION:
y = {distribution=normal, prediction=Cc, errorModel=combined1(add, prop)}
")

ivmfood.params.fasted <- data.frame(
  Cl_pop = 7.74, Cl_sd = sqrt(0.31), 
  V1_pop = 100.8, V1_sd = sqrt(0.1),
  V2_pop = 228.8, V2_sd = sqrt(0.21),
  Q_pop = 18.67, Q_sd = sqrt(0.52),
  ka_pop = 0.68, ka_sd = 0,
  Mtt_pop = 0.93, Mtt_sd = sqrt(0.63),
  NN_pop = 6, NN_sd = 0,
  F1_pop = 0.84,
  prop = 0.09, 
  add = 0.82,
  WT = 70
)

ivmfood.params.fed <- ivmfood.params.fasted %>% mutate(F1_pop=1)
```


```{r echo=F}
##### 3x600 ug/kg, 70 kg
set.seed(1234)

study_h = 40*24
study_n = 1 #length(covid.population$WT)
study_tp = c(seq(0, study_h, by=1) )
y <- list(name='y', time=study_tp )
Cc <- list(name='Cc', time=study_tp )

# typical patient -> no IIV
covid.ivmfood.params <- data.frame(
  id = 1,
  Cl_pop = 7.74, Cl_sd = 0,
  V1_pop = 100.8, V1_sd = 0,
  V2_pop = 228.8, V2_sd = 0,
  Q_pop = 18.67, Q_sd = 0,
  ka_pop = 0.68, ka_sd = 0,
  Mtt_pop = 0.93, Mtt_sd = 0,
  NN_pop = 6, NN_sd = 0,
  F1_pop = 1, # fed
  prop = 0.09, 
  add = 0.82,
  WT = 70
)

adm  <- data.frame( id=1,
                    amount=rep( 600*70, 3),
                    time = c(0, 24, 48) )

# n=sim_rep replicates of trial
covid.sim.ivmfood.3x600.typical <- simulx( model = ivmfood.model,
                                           output = list(Cc, y),
                                           parameter = covid.ivmfood.params,
                                           treatment = adm )

ggplot(covid.sim.ivmfood.3x600.typical$Cc %>% 
         dplyr::filter( time<7*24), aes(time, Cc)) +
  geom_line() +
  labs( title=sprintf("IVM 3x600 ug/kg typical individual"),
        subtitle="Model: IVMFood (Duthaler, JAC 2020)",
        x = "Time [h]",
        y = "Concentration [ng/mL]") +
  scale_x_continuous( breaks = (0:7)*24 )
#theme_ipsum_ps() 
```


#### Mode of action
```{r}
IVM_MW <- 875.1 # g/mol, for conversion to uM

LUNG_ACCUMULATION <- 2.6 # cattle lung accumulation, Ref: Lifschitz
IVM_unbound_fraction <- (1-0.93) #93% of drug is protein bound

nAChR_IC50_uM <- 156 / 1000 #https://www.nature.com/articles/srep42481
nAChR_Hill <- 1

# Helicase inhibition
# Ref: J Antimicrob Chemother. 2012 Aug;67(8):1884-94.
# doi: 10.1093/jac/dks147. Epub 2012 Apr 25. https://pubmed.ncbi.nlm.nih.gov/22535622/
YFV_IC50_uM <- 0.12 # +/- 0.01
DENV_IC50_uM <- 0.5 # +/- 0.07
WNV_IC50_uM <- 0.35 # +/- 0.04
HELICASE_IC50_uM <- 0.25 # estimate
HELICASE_IC50_uM <- 0.1 # 10 fold higher IC50 in Vero, so 10 fold lower IC50 for helicase
```

```{r echo=F, fig.width=12, fig.height=5}
# drug effects go here. First convert to uM, then relate to PK/PD behavior
covid.sim.ivmfood.3x600.typical$Cc %<>% 
  mutate( CC_umol = Cc / IVM_MW ) %>% 
  mutate( eps_nAChR = CC_umol/(nAChR_IC50_uM+CC_umol),
          eps_nAChR_lung = LUNG_ACCUMULATION*CC_umol/(nAChR_IC50_uM+LUNG_ACCUMULATION*CC_umol),
          # eps_nAChR_unbound = IVM_unbound_fraction*CC_umol/ (nAChR_IC50_uM+CC_umol*IVM_unbound_fraction),
          eps_nAChR_unbound = LUNG_ACCUMULATION*IVM_unbound_fraction*CC_umol/ (nAChR_IC50_uM+LUNG_ACCUMULATION*CC_umol*IVM_unbound_fraction),
          eps_helicase = CC_umol/(HELICASE_IC50_uM+CC_umol),
          eps_helicase_lung = LUNG_ACCUMULATION*CC_umol/(HELICASE_IC50_uM+LUNG_ACCUMULATION*CC_umol),
          # eps_helicase_unbound = CC_umol*IVM_unbound_fraction/ (HELICASE_IC50_uM+CC_umol*IVM_unbound_fraction))
          eps_helicase_unbound = LUNG_ACCUMULATION*CC_umol*IVM_unbound_fraction/ (HELICASE_IC50_uM+LUNG_ACCUMULATION*CC_umol*IVM_unbound_fraction))

p.eps.nAChR <- ggplot( covid.sim.ivmfood.3x600.typical$Cc %>% 
                         filter( time < 7*24 ), aes( time, eps_nAChR) ) +
  geom_line() +
  geom_line(aes(time, eps_nAChR_lung), linetype="dotted") +
  geom_line(aes(time, eps_nAChR_unbound), linetype="dashed") +
  labs( title=sprintf("IVM 3x600 ug/kg typical individual"),
        subtitle="inhibitory effect on nAChR",
        x = "Time [h]",
        y = "Inhibition") +
  scale_x_continuous( breaks = (0:7)*24 )
#theme_ipsum_ps() 

p.eps.helicase <- ggplot( covid.sim.ivmfood.3x600.typical$Cc %>% 
                            filter( time < 7*24 ), aes( time, eps_helicase) ) +
  geom_line() +
  labs( title=sprintf("IVM 3x600 ug/kg typical individual"),
        subtitle="inhibitory effect helicase",
        x = "Time [h]",
        y = "Inhibition (eps)") +
  scale_x_continuous( breaks = (0:7)*24 )
#theme_ipsum_ps() 

gridExtra::grid.arrange(p.eps.nAChR, p.eps.helicase, nrow=1  )
```


# Results
## Viral kinetics models
### Target cell limited models

### Nelder Mead estimated parameters
from script Nelder_Mead_final.Rmd
```{r}

TIME_POSITIVITY <- 5.4*24 #days post infection
TIME_PRESENTATION <- 10.2*24 #days post infection

get_ode_states_parameters <- function(R0, immune_response="RBD_To" ) { 
  c <- 5.07 #5.6 #Nelder Mead #3 # virus clearance
  delta <- 0.54 #0.4 #Nelder Mead #0.8 # cell death
  p <- 10.18 #9.6 #Nelder Mead #12 # viral production rate
  I0 <- 0 # number of infected cells
  T0 <- 1*10**5 # number of target cells
  #R0 <- R0#3.79 # within-host reproduction number
  V0 <- 1 #Nelder Mead #10**(-1) # initial load (inoculum)
  
  Immune_EC50 <- IgG_RBD_To_EC50 # days
  Immune_Hill <- IgG_RBD_To_Hill # Hill coefficient
  Immune_Emax <- IgG_RBD_To_max_eps # maximum effect on viral clearance
  
  if( immune_response == "Sero_Long" ) {
    Immune_EC50 <- IgG_Long_EC50 # days
    Immune_Hill <- IgG_Long_Hill # Hill coefficient
    Immune_Emax <- IgG_Long_max_eps # maximum effect on viral clearance    
  }
  
  beta <- c *delta*R0/((p-delta*R0)*T0)
  
  # ODE system parameterization
  parameters <- c( c=c,
                   delta=delta,
                   p=p,
                   R0=R0,
                   beta=beta,
                   T0 = T0, #VS: T0 added here, as otherwise error "T0 is missing"
                   Immune_EC50=Immune_EC50,
                   Immune_Emax=Immune_Emax,
                   Immune_Hill=Immune_Hill)
  
  # ODE system initial conditions
  state <- c( Tf = T0, # target cells
              If = I0, # infected cells
              Vf = V0 ) # viral load
  
  return( list(state=state, parameters=parameters))
} 

get_ode_states_parameters(R0=3.79)
get_ode_states_parameters(R0=3.79,"RBD_To")
get_ode_states_parameters(R0=3.79,"Sero_Long")
```

```{r echo=F}
times <- seq(0, 40, # number of days
             by = .1) 

input_inf <- input_cl <- input_repro <- function(x) return(0) # set all effects to 0 at any time

# model
sars2_noeclipse <- function( t, state, parameters ) {  # function of time, state, parameters
  with(as.list(c(state, parameters)),{ 
    # rate of change
    eps_inf <- input_inf(t)
    eps_repro <- input_repro(t)
    eps_acquired <- Immune_Emax * (t^Immune_Hill)/(Immune_EC50^Immune_Hill+t^Immune_Hill)
    beta <- c*(1+eps_acquired)*delta*R0/((p-delta*R0)*T0) #FELIX: where does the p-delta*R0 come from?
    # beta <- c*(1+eps_acquired)*delta*R0/(p*T0) #VS came to this formula. Anyways, should eps not be be between 0 and 1? Why is it 42
    
    dTf <-  - beta*(1-eps_inf)*Tf*Vf
    dIf <-  + beta*(1-eps_inf)*Tf*Vf - delta*If
    dVf <-  + p*(1-eps_repro)*If - c*(1+eps_acquired)*Vf - beta*(1-eps_inf)*Tf*Vf
    # return rate of change
    list(c(dTf, dIf, dVf))
  })
}

# R0 as in Kern et al. 2020
ode_settings <- get_ode_states_parameters(R0=3.79,immune_response = "Sero_Long")

df.regular <- ode(y = ode_settings$state, 
                  times = times, 
                  func = sars2_noeclipse, 
                  parms = ode_settings$parameters) %>% 
  as.data.frame() %>% 
  mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
          group="R0")

#R0 double
ode_settings <- get_ode_states_parameters(R0=3.79*2, "Sero_Long")

df.double <- ode(y = ode_settings$state, 
                 times = times, 
                 func = sars2_noeclipse, 
                 parms = ode_settings$parameters) %>% 
  as.data.frame() %>% 
  mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
          group="R0*2")

#R0 half
ode_settings <- get_ode_states_parameters(R0=3.79*0.75, "Sero_Long")

df.threequarter <- ode(y = ode_settings$state, 
                       times = times, 
                       func = sars2_noeclipse, 
                       parms = ode_settings$parameters) %>% 
  as.data.frame() %>% 
  mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
          group="R0*0.75")

#R0 quadruple
ode_settings <- get_ode_states_parameters(R0=3.79*1.25, "Sero_Long")


df.oneandquarter <- ode(y = ode_settings$state, 
                        times = times, 
                        func = sars2_noeclipse, 
                        parms = ode_settings$parameters) %>% 
  as.data.frame() %>% 
  mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
          group="R0*1.25")

#R0 quadruple
ode_settings <- get_ode_states_parameters(R0=3.79*1.5, "Sero_Long")


df.oneandhalf <- ode(y = ode_settings$state, 
                     times = times, 
                     func = sars2_noeclipse, 
                     parms = ode_settings$parameters) %>% 
  as.data.frame() %>% 
  mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
          group="R0*1.5")
```

#### ** Summary plot
```{r echo=F}
ggplot( rbind(df.regular,
              df.double,
              df.threequarter,
              df.oneandhalf,
              df.oneandquarter) %>% filter(time<30 & Ct < 43), aes(time, Ct, group=group, color=group)) + #color=group, JAC was Black/White graphs
  geom_hline( yintercept = CT_LIMIT_OF_DETECTION, linetype="dotted", color="black", size=.5 ) +
  geom_line(size=1) +
  scale_y_continuous( breaks=(0:10)*5, trans="reverse") + # flip y axis because low Ct values are bad
  labs( color="",
        linetype="",
        x="Days post infection (dpi) [d]",
        y="Viral load [Ct]") +
  #theme_ipsum_ps() +
  theme( legend.position = "bottom") +
  scale_colour_manual(values = c( "R0"="black", "R0*2"="indianred3", "R0*1.5"="indianred2", "R0*1.25"="orange1", "R0*0.75"="royalblue3"))
```

#### ** Summary table natural history
```{r}
df.natural <- rbind(df.regular,
                    df.double,
                    df.threequarter,
                    df.oneandhalf,
                    df.oneandquarter) 

df.natural.summary <- merge( 
  df.natural %>% 
    group_by(group) %>% 
    filter( Ct < CT_LIMIT_OF_DETECTION ) %>% 
    summarise( start_positivity = min(time),
               duration = max(time)-min(time),
               min_Ct = min(Ct)),
  df.natural %>% 
    group_by( group ) %>% 
    summarise( AUC = LinAUC( x=time, y=Vf)["AUC"] ),
  by="group")

df.natural.summary
```

## Linking PK and viral kinetics (RGB_To)
### Ivermectin 3x600 ug/kg
#### Simulations

```{r}
time_offset <- seq.int(-48, 7*24, by =24 )
```

##### R0*1
```{r}
df.3x600.regular <- data.frame(time=numeric(),
                               Tf=numeric(),
                               If=numeric(),
                               Vf=numeric(),
                               Ct=numeric(),
                               group=character()) 

#time_offset = seq.int(-48, 120, by =1 )

#Define R0 here!
R0_mod=3.79

for (i in 1:length(time_offset)){
  
  time_mod <- time_offset[i]
  
  ode_settings <- get_ode_states_parameters(R0=R0_mod, immune_response = "Sero_Long")
  
  times <- seq(0, 40, # number of days
               by = .1) 
  
  input_inf <- input_cl <- input_repro <- function(x) return(0) # set all effects to 0 at any time
  
  if (time_mod<=0){
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      filter(time>=abs (time_mod)) %>% 
      mutate (time = time - abs(time_mod))
  } else {
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      mutate (time = time +time_mod)
    df <- rbind( data.frame( time=0, 
                             Cc=0,
                             CC_umol=0,
                             eps_nAChR=0,
                             eps_nAChR_lung=0,
                             eps_nAChR_unbound=0,
                             eps_helicase=0,
                             eps_helicase_lung=0,
                             eps_helicase_unbound=0),
                 df )
  }
  
  input_repro <- approxfun( df$time/24, df$eps_helicase_unbound) # effect of helicase suppression
  input_inf <- approxfun( df$time/24, df$eps_nAChR_unbound) # effect of infectivity suppression
  
  b <- ode(y = ode_settings$state, #dbi days before inoculation
           times = times,
           func = sars2_noeclipse,
           parms = ode_settings$parameters) %>%
    as.data.frame() %>%
    mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
            group=paste (time_mod, " hours, R0*1", sep=""))
  
  df.3x600.regular <- rbind (b, df.3x600.regular)
}
```

##### R0*0.75
```{r}
df.3x600.coadapt <- data.frame(time=numeric(),
                               Tf=numeric(),
                               If=numeric(),
                               Vf=numeric(),
                               Ct=numeric(),
                               group=character()) 

#Define R0 here!
R0_mod=3.79*0.75

for (i in 1:length(time_offset)){
  
  time_mod = time_offset[i]
  
  ode_settings <- get_ode_states_parameters(R0=R0_mod, immune_response = "Sero_Long")
  
  times <- seq(0, 40, # number of days
               by = .1) 
  
  input_inf <- input_cl <- input_repro <- function(x) return(0) # set all effects to 0 at any time
  
  if (time_mod<=0){
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      filter(time>=abs (time_mod)) %>% 
      mutate (time = time - abs(time_mod))
  } else {
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      mutate (time = time +time_mod)
    df <- rbind( data.frame( time=0, 
                             Cc=0,
                             CC_umol=0,
                             eps_nAChR=0,
                             eps_nAChR_lung=0,
                             eps_nAChR_unbound=0,
                             eps_helicase=0,
                             eps_helicase_lung=0,
                             eps_helicase_unbound=0),
                 df )
  }
  
  input_repro <- approxfun( df$time/24, df$eps_helicase_unbound) # effect of helicase suppression
  input_inf <- approxfun( df$time/24, df$eps_nAChR_unbound) # effect of infectivity suppression
  
  b   <- ode(y = ode_settings$state, #dbi days before inoculation
             times = times,
             func = sars2_noeclipse,
             parms = ode_settings$parameters) %>%
    as.data.frame() %>%
    mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
            group=paste (time_mod, " hours, R0*0.75", sep=""))
  
  df.3x600.coadapt <- rbind (b, df.3x600.coadapt)
  
}
```

##### R0*1.25
```{r}
df.3x600.high_25 <- data.frame(time=numeric(),
                               Tf=numeric(),
                               If=numeric(),
                               Vf=numeric(),
                               Ct=numeric(),
                               group=character()) 

#Define R0 here!
R0_mod=3.79*1.25

for (i in 1:length(time_offset)){
  
  time_mod = time_offset[i]
  
  ode_settings <- get_ode_states_parameters(R0=R0_mod, immune_response = "Sero_Long")
  
  times <- seq(0, 40, # number of days
               by = .1) 
  
  input_inf <- input_cl <- input_repro <- function(x) return(0) # set all effects to 0 at any time
  
  if (time_mod<=0){
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      filter(time>=abs (time_mod)) %>% 
      mutate (time = time - abs(time_mod))
  } else {
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      mutate (time = time +time_mod)
    df <- rbind( data.frame( time=0, 
                             Cc=0,
                             CC_umol=0,
                             eps_nAChR=0,
                             eps_nAChR_lung=0,
                             eps_nAChR_unbound=0,
                             eps_helicase=0,
                             eps_helicase_lung=0,
                             eps_helicase_unbound=0),
                 df )
  }
  
  input_repro <- approxfun( df$time/24, df$eps_helicase_unbound) # effect of helicase suppression
  input_inf <- approxfun( df$time/24, df$eps_nAChR_unbound) # effect of infectivity suppression
  
  b   <- ode(y = ode_settings$state, #dbi days before inoculation
             times = times,
             func = sars2_noeclipse,
             parms = ode_settings$parameters) %>%
    as.data.frame() %>%
    mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
            group=paste (time_mod, " hours, R0*1.25", sep=""))
  
  df.3x600.high_25 <- rbind (b, df.3x600.high_25)
  
}
```

##### R0*1.5
```{r}
df.3x600.high_50 <- data.frame(time=numeric(),
                               Tf=numeric(),
                               If=numeric(),
                               Vf=numeric(),
                               Ct=numeric(),
                               group=character()) 

#Define R0 here!
R0_mod=3.79*1.5

for (i in 1:length(time_offset)){
  
  time_mod = time_offset[i]
  
  ode_settings <- get_ode_states_parameters(R0=R0_mod, immune_response = "Sero_Long")
  
  times <- seq(0, 40, # number of days
               by = .1) 
  
  input_inf <- input_cl <- input_repro <- function(x) return(0) # set all effects to 0 at any time
  
  if (time_mod<=0){
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      filter(time>=abs (time_mod)) %>% 
      mutate (time = time - abs(time_mod))
  } else {
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      mutate (time = time +time_mod)
    df <- rbind( data.frame( time=0, 
                             Cc=0,
                             CC_umol=0,
                             eps_nAChR=0,
                             eps_nAChR_lung=0,
                             eps_nAChR_unbound=0,
                             eps_helicase=0,
                             eps_helicase_lung=0,
                             eps_helicase_unbound=0),
                 df )
  }
  
  input_repro <- approxfun( df$time/24, df$eps_helicase_unbound) # effect of helicase suppression
  input_inf <- approxfun( df$time/24, df$eps_nAChR_unbound) # effect of infectivity suppression
  
  b   <- ode(y = ode_settings$state, #dbi days before inoculation
             times = times,
             func = sars2_noeclipse,
             parms = ode_settings$parameters) %>%
    as.data.frame() %>%
    mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
            group=paste (time_mod, " hours, R0*1.5", sep=""))
  
  df.3x600.high_50 <- rbind (b, df.3x600.high_50)
  
}
```

##### R0*2
```{r}
df.3x600.high_100 <- data.frame(time=numeric(),
                                Tf=numeric(),
                                If=numeric(),
                                Vf=numeric(),
                                Ct=numeric(),
                                group=character()) 

#Define R0 here!
R0_mod=3.79*2

for (i in 1:length(time_offset)){
  
  time_mod = time_offset[i]
  
  ode_settings <- get_ode_states_parameters(R0=R0_mod, immune_response = "Sero_Long")
  
  times <- seq(0, 40, # number of days
               by = .1) 
  
  input_inf <- input_cl <- input_repro <- function(x) return(0) # set all effects to 0 at any time
  
  if (time_mod<=0){
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      filter(time>=abs (time_mod)) %>% 
      mutate (time = time - abs(time_mod))
  } else {
    df <- covid.sim.ivmfood.3x600.typical$Cc %>% 
      mutate (time = time +time_mod)
    df <- rbind( data.frame( time=0, 
                             Cc=0,
                             CC_umol=0,
                             eps_nAChR=0,
                             eps_nAChR_lung=0,
                             eps_nAChR_unbound=0,
                             eps_helicase=0,
                             eps_helicase_lung=0,
                             eps_helicase_unbound=0),
                 df )
  }
  
  input_repro <- approxfun( df$time/24, df$eps_helicase_unbound) # effect of helicase suppression
  input_inf <- approxfun( df$time/24, df$eps_nAChR_unbound) # effect of infectivity suppression
  
  b   <- ode(y = ode_settings$state, #dbi days before inoculation
             times = times,
             func = sars2_noeclipse,
             parms = ode_settings$parameters) %>%
    as.data.frame() %>%
    mutate( Ct = Ct_viral_load( viral_load=log(Vf,base=10) ),
            group=paste (time_mod, " hours, R0*2", sep=""))
  
  df.3x600.high_100 <- rbind (b, df.3x600.high_100)
  
}
```

####Summary
##### Regular
```{r echo=F}
df.3x600.regular.summary <- rbind(df.regular %>% mutate(group="untreated R0*1"), 
                                  df.3x600.regular) %>% 
  filter(time<30)

df.3x600.regular.summary <-merge( df.3x600.regular.summary %>% 
                                    group_by( group ) %>% 
                                    filter( Ct < CT_LIMIT_OF_DETECTION ) %>% 
                                    summarise( start_positivity = min(time),
                                               duration = max(time)-min(time),
                                               min_Ct = min(Ct)),
                                  df.3x600.regular.summary %>% 
                                    group_by( group ) %>% 
                                    summarise( AUC = LinAUC( x=time, y=Vf)["AUC"] ),
                                  by="group" )

df.3x600.regular.summary %<>%
  mutate(start_pos_rel = start_positivity-start_positivity[group=="untreated R0*1"],
         duration_rel = duration -duration[group=="untreated R0*1"],
         min_Ct_rel = round(min_Ct / min_Ct[group=="untreated R0*1"],4),
         AUC_rel = round(AUC / AUC[group=="untreated R0*1"],4))
```
##### R0*0.75

```{r echo=F}
df.3x600.coadapt.summary <- rbind(df.threequarter %>% mutate(group="untreated R0*0.75"), 
                                  df.3x600.coadapt) %>% 
  filter(time<30)

df.3x600.coadapt.summary <-merge( df.3x600.coadapt.summary %>% 
                                    group_by( group ) %>% 
                                    filter( Ct < CT_LIMIT_OF_DETECTION ) %>% 
                                    summarise( start_positivity = min(time),
                                               duration = max(time)-min(time),
                                               min_Ct = min(Ct)),
                                  df.3x600.coadapt.summary %>% 
                                    group_by( group ) %>% 
                                    summarise( AUC = LinAUC( x=time, y=Vf)["AUC"] ),
                                  by="group" )

df.3x600.coadapt.summary %<>%
  mutate(start_pos_rel = start_positivity-start_positivity[group=="untreated R0*0.75"],
         duration_rel = duration -duration[group=="untreated R0*0.75"],
         min_Ct_rel = round(min_Ct / min_Ct[group=="untreated R0*0.75"],4),
         AUC_rel = round(AUC / AUC[group=="untreated R0*0.75"],4))
```

##### R0*1.25
```{r echo=F}
df.3x600.high_25.summary <- rbind(df.oneandquarter %>% mutate(group="untreated R0*1.25"), 
                                  df.3x600.high_25) %>% 
  filter(time<30)

df.3x600.high_25.summary <-merge( df.3x600.high_25.summary %>% 
                                    group_by( group ) %>% 
                                    filter( Ct < CT_LIMIT_OF_DETECTION ) %>% 
                                    summarise( start_positivity = min(time),
                                               duration = max(time)-min(time),
                                               min_Ct = min(Ct)),
                                  df.3x600.high_25.summary %>% 
                                    group_by( group ) %>% 
                                    summarise( AUC = LinAUC( x=time, y=Vf)["AUC"] ),
                                  by="group" )

df.3x600.high_25.summary %<>%
  mutate(start_pos_rel = start_positivity-start_positivity[group=="untreated R0*1.25"],
         duration_rel = duration -duration[group=="untreated R0*1.25"],
         min_Ct_rel = round(min_Ct / min_Ct[group=="untreated R0*1.25"],4),
         AUC_rel = round(AUC / AUC[group=="untreated R0*1.25"],4))
```

##### R0*1.5
```{r echo=F}
df.3x600.high_50.summary <- rbind(df.oneandhalf %>% mutate(group="untreated R0*1.5"), 
                                  df.3x600.high_50) %>% 
  filter(time<30)

df.3x600.high_50.summary <-merge( df.3x600.high_50.summary %>% 
                                    group_by( group ) %>% 
                                    filter( Ct < CT_LIMIT_OF_DETECTION ) %>% 
                                    summarise( start_positivity = min(time),
                                               duration = max(time)-min(time),
                                               min_Ct = min(Ct)),
                                  df.3x600.high_50.summary %>% 
                                    group_by( group ) %>% 
                                    summarise( AUC = LinAUC( x=time, y=Vf)["AUC"] ),
                                  by="group" )

df.3x600.high_50.summary %<>%
  mutate(start_pos_rel = start_positivity-start_positivity[group=="untreated R0*1.5"],
         duration_rel = duration -duration[group=="untreated R0*1.5"],
         min_Ct_rel = round(min_Ct / min_Ct[group=="untreated R0*1.5"],4),
         AUC_rel = round(AUC / AUC[group=="untreated R0*1.5"],4))
```

##### R0*2
```{r echo=F}
df.3x600.high_100.summary <- rbind(df.double %>% mutate(group="untreated R0*2"), 
                                   df.3x600.high_100) %>% 
  filter(time<30)

df.3x600.high_100.summary <-merge( df.3x600.high_100.summary %>% 
                                     group_by( group ) %>% 
                                     filter( Ct < CT_LIMIT_OF_DETECTION ) %>% 
                                     summarise( start_positivity = min(time),
                                                duration = max(time)-min(time),
                                                min_Ct = min(Ct)),
                                   df.3x600.high_100.summary %>% 
                                     group_by( group ) %>% 
                                     summarise( AUC = LinAUC( x=time, y=Vf)["AUC"] ),
                                   by="group" )

df.3x600.high_100.summary %<>%
  mutate(start_pos_rel = start_positivity-start_positivity[group=="untreated R0*2"],
         duration_rel = duration -duration[group=="untreated R0*2"],
         min_Ct_rel = round(min_Ct / min_Ct[group=="untreated R0*2"],4),
         AUC_rel = round(AUC / AUC[group=="untreated R0*2"],4))

```

# ** Summary all
```{r}
df.sum.all <- rbind(df.3x600.regular.summary,
                    df.3x600.coadapt.summary,
                    df.3x600.high_25.summary,
                    df.3x600.high_50.summary,
                    df.3x600.high_100.summary)


df.sum.all %<>%                
  mutate(timing = (as.numeric (gsub( " .*$", "", group )))/24, #takes everything after space and replaces it with nothing
         # ),
         R0 = as.factor(round(as.numeric (gsub (".*\\*","", group)),2))) #takes everything before * and replaces it with nothing

df.sum.all

```

## Grid plots
```{r}
p1 <- ggplot(df.sum.all %>% filter(timing!="untreated") %>% 
               mutate(R0=paste("R0*", R0, sep="")),
             aes(x=timing, y=duration_rel, group= R0, colour=R0)) +
  geom_line(size=1) +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(title="Change in duration", 
       x = "Treatment initiation [dpi]", 
       y="Duration [days]",
       color="") + 
  #theme_ipsum_ps() + 
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks=(-2:7)) +
  scale_colour_manual(values = c( "R0*1"="black", "R0*2"="indianred3", "R0*1.5"="indianred2", "R0*1.25"="orange1", "R0*0.75"="royalblue3"))+
  theme(text = element_text(size=15),
        axis.text.x = element_text(size=11),
        axis.text.y  = element_text(size=11),
        axis.title.x = element_text(size=13),
        axis.title.y = element_text(size=13))

p2 <- ggplot(df.sum.all %>% filter(timing!="untreated") %>% 
               mutate(R0=paste("R0*", R0, sep="")),
             aes(x=timing, y=1-AUC_rel, group= R0, colour=R0)) +
  geom_line(size=1) +
  labs(title="Relative decrease in AUC", 
       x = "Treatment initiation [dpi]", 
       y="Change in AUC [%]",
       color="") + 
  #theme_ipsum_ps() + 
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks=(-2:7)) +
  scale_y_continuous(limits=c(0, .45), labels = scales::percent_format(accuracy = 1)) +
  scale_colour_manual(values = c( "R0*1"="black", "R0*2"="indianred3", "R0*1.5"="indianred2", "R0*1.25"="orange1", "R0*0.75"="royalblue3"))+
  theme(text = element_text(size=15),
        axis.text.x = element_text(size=11),
        axis.text.y  = element_text(size=11),
        axis.title.x = element_text(size=13),
        axis.title.y = element_text(size=13))


p3 <- ggplot(df.sum.all %>% filter(timing!="untreated") %>% 
               mutate(R0=paste("R0*", R0, sep="")),
             aes(x=timing, y=min_Ct_rel, group= R0, colour=R0)) +
  geom_line(size=1) +
  labs(title="Change in peak Ct", 
       x = "Treatment initiation [dpi]", 
       y = "Cycles",
       color="") + 
  #theme_ipsum_ps() + 
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks=(-2:7)) +
  scale_colour_manual(values = c( "R0*1"="black", "R0*2"="indianred3", "R0*1.5"="indianred2", "R0*1.25"="orange1", "R0*0.75"="royalblue3"))


p1
p2
p3 

```

```{r, fig.width=7, fig.height=3}

g2 <- grid.arrange(p2+labs(title="a)"), p1+labs(title="b)"), #p3,
                   ncol =2)  
g2
```



